Query Optimization for Dynamic Imputation

### 2017-02-28 paper/experiments.tex
Move planing times results to commands

In the median query across a variety of queries and choices of $\alpha$, planning
constituted 8.5 percent of total runtime. In all cases, the optimizer
returned a query plan within 40ms, with times roughly constant between levels of $\alpha$.

>>>>

In the median query across a variety of queries and choices of $\alpha$, planning
constituted \planningruntimepercent{} percent of total runtime. In all cases, the optimizer
returned a query plan within \planningmaxtime{} ms, with times roughly constant between levels of $\alpha$.
